Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-09-01 WSSSPE3/report/wg_main_user_community.tex
fixing a typo

There are a number of activities already in progress that are targeted at improving
the user community for open-source software, including Mozilla Science's ``Working Open Project
Guide''~\cite{working-open-wssspe3} and
``UK Collaborative Computational Projects'' (CCP)\footnote{\url{http://www.ccp.ac.uk)}}, or 
 books such as ``Art of Community'' by Jono Bacon~\cite{art-of-community}.

>>>>

There are a number of activities already in progress that are targeted at improving
the user community for open-source software, including Mozilla Science's ``Working Open Project
Guide''~\cite{working-open-wssspe3} and
``UK Collaborative Computational Projects'' (CCP)\footnote{\url{http://www.ccp.ac.uk}}, or 
 books such as ``Art of Community'' by Jono Bacon~\cite{art-of-community}.
